Improved Particle Approximations \\ to the Joint Smoothing Distribution \\ Using Markov Chain Monte Carlo

### 2013-11-28 Paper/complete/12-11-14_final_submission/double_MCMCsmoother.tex
Added clean version of code.

\documentclass[peerreview,11pt,draftcls,onecolumn]{IEEEtran}

%% Packages
\usepackage{cite}
\usepackage[pdftex]{graphicx} \graphicspath{{images/}}
\usepackage[cmex10]{amsmath}
%\usepackage{algorithm}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
%\usepackage{stfloats}
\usepackage{url}
\usepackage{color}

\newenvironment{meta}[0]{\color{red} \em}{}

% correct bad hyphenation here
\hyphenation{}

@@

\author{Pete~Bunch*,~\IEEEmembership{Member,~IEEE,} and
        Simon~Godsill,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{P. Bunch and S. Godsill are with the Department
of Engineering, Cambridge University, UK. email: \{pb404,sjg30\}@cam.ac.uk}% <-this % stops a space
\thanks{Manuscript received April 03, 2012.}}

%% The paper headers
%\markboth{IEEE Transactions on Signal Processing,~Vol.~AA, No.~BB, January~YYYY}%
%{MCMC Particle Smoothing Approximations}

@@

%\begin{IEEEkeywords}
%state space model, particle filter, smoothing, MCMC, Bayesian inference
%\end{IEEEkeywords}

\ifCLASSOPTIONpeerreview
\begin{center} \bfseries EDICS Categories: MLR-BAYL, SSP-NGAU, SSP-TRAC, SSP-FILT \end{center}
\fi

\newpage
% For peerreview papers, this IEEEtran command inserts a page break and
% creates the second title. It will be ignored for other modes.
%\IEEEpeerreviewmaketitle

@@

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_trajectory.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_trajectory.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.45\columnwidth]{case3_trajectory.pdf}}
\caption{Example trajectory with observations from the two noise covariance cases. Constant likelihood contours are shown for the first and last position (dashed)}
\label{fig:example_trajectories}
\end{figure}

@@

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 1. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 0.56 & 0.96 & 0.99 & 0.00 & 2.13 \\
D-FFBS         & 0.45 & 0.76 & 0.84 & 65.88 & 20.54 \\
\hline
MH-FFBS (1)    & 0.48 & 0.81 & 0.90 & 1.80 & 13.95 \\
MH-FFBS (3)    & 0.46 & 0.78 & 0.87 & 3.89 & 17.63 \\
MH-FFBS (10)   & 0.46 & 0.77 & 0.85 & 11.20 & 19.83 \\
MH-FFBS (30)   & 0.45 & 0.76 & 0.84 & 32.05 & 20.40 \\
MH-FFBS (100)  & 0.45 & 0.76 & 0.84 & 105.12 & 20.55 \\
\hline
MH-FFBP (1)    & 0.45 & 0.75 & 0.82 & 9.20 & 44.32 \\
MH-FFBP (3)    & 0.43 & 0.73 & 0.79 & 19.23 & 70.12 \\
MH-FFBP (10)   & 0.43 & 0.72 & 0.78 & 54.33 & 90.10 \\
MH-FFBP (30)   & 0.42 & 0.71 & 0.79 & 154.47 & 96.89 \\
MH-FFBP (100)  & 0.42 & 0.70 & 0.79 & 504.58 & 98.53 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 2. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 8.01 & 1.90 & 0.99 & 0.00 & 2.75 \\
D-FFBS         & 7.71 & 1.70 & 0.92 & 66.40 & 14.06 \\
\hline
MH-FFBS (1)    & 7.91 & 1.83 & 0.98 & 1.79 & 6.51 \\
MH-FFBS (3)    & 7.83 & 1.78 & 0.96 & 3.86 & 8.63 \\
MH-FFBS (10)   & 7.77 & 1.73 & 0.93 & 11.09 & 11.39 \\
MH-FFBS (30)   & 7.75 & 1.71 & 0.92 & 31.77 & 13.14 \\
MH-FFBS (100)  & 7.70 & 1.70 & 0.92 & 104.14 & 13.88 \\
\hline
MH-FFBP (1)    & 7.75 & 1.72 & 0.92 & 9.25 & 22.97 \\
MH-FFBP (3)    & 7.67 & 1.67 & 0.88 & 19.34 & 42.22 \\
MH-FFBP (10)   & 7.62 & 1.63 & 0.85 & 54.61 & 70.06 \\
MH-FFBP (30)   & 7.60 & 1.61 & 0.84 & 155.38 & 88.81 \\
MH-FFBP (100)  & 7.59 & 1.60 & 0.84 & 507.58 & 96.82 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 3. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case3_performance}
{\scriptsize
\begin{center}
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS            & 7.41 & 2.15 & 0.98 & 0.00 & 3.97 \\
D-FFBS        & 7.19 & 2.03 & 0.97 & 66.27 & 7.48 \\
\hline
MH-FFBS (1)   & 7.39 & 2.14 & 0.98 & 1.75 & 4.79 \\
MH-FFBS (3)   & 7.36 & 2.12 & 0.98 & 3.75 & 5.33 \\
MH-FFBS (10)  & 7.30 & 2.08 & 0.98 & 10.78 & 6.16 \\
MH-FFBS (30)  & 7.24 & 2.05 & 0.97 & 30.83 & 6.88 \\
MH-FFBS (100) & 7.20 & 2.04 & 0.97 & 101.02 & 7.38 \\
\hline
MH-FFBP (1)   & 7.22 & 2.05 & 0.97 & 9.12 & 12.57 \\
MH-FFBP (3)   & 7.08 & 1.98 & 0.94 & 19.01 & 22.78 \\
MH-FFBP (10)  & 6.95 & 1.92 & 0.92 & 53.64 & 44.15 \\
MH-FFBP (30)  & 6.87 & 1.88 & 0.90 & 152.42 & 70.71 \\
MH-FFBP (100) & 6.84 & 1.86 & 0.88 & 498.38 & 91.35 \\
\hline
\end{tabular}
\end{center}
}
\end{table}

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.45\columnwidth]{case1_smoother_comparison_posRMSE_time.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.45\columnwidth]{case2_smoother_comparison_posRMSE_time.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.45\columnwidth]{case3_smoother_comparison_posRMSE_time.pdf}}
\caption{Position RMSEs and running times of various smoothing algorithms with different noise covariance cases.}%
\label{fig:rmse_vs_time}%
\end{figure}

@@

%\section{Appendix Title}
%Appendix one text goes here.

%\section*{Acknowledgment}
%The authors would like to thank...

\newpage
\bibliographystyle{IEEEtran}
\bibliography{D:/pb404/Dropbox/PhD/Cleanbib}

@@

%\input{D:/pb404/Dropbox/PhD/Biographies/IEEE-Bunch.tex}
%\input{D:/pb404/Dropbox/PhD/Biographies/IEEE-Godsill.tex}

>>>>

\documentclass[10pt,twocolumn,twoside]{IEEEtran}

%% Packages
\usepackage{cite}
\usepackage[pdftex]{graphicx}
\usepackage[cmex10]{amsmath}
\usepackage{algorithmic}
\usepackage{array}
\usepackage{mdwmath}
\usepackage{mdwtab}
\usepackage{eqparbox}
\usepackage[caption=false,font=footnotesize]{subfig}
\usepackage{fixltx2e}
\usepackage{url}
\usepackage{color}

@@

\author{Pete~Bunch*,~\IEEEmembership{Member,~IEEE,} and
        Simon~Godsill,~\IEEEmembership{Member,~IEEE}% <-this % stops a space
\thanks{Copyright (c) 2012 IEEE. Personal use of this material is permitted. However, permission to use this material for any other purposes must be obtained from the IEEE by sending a request to pubs-permissions@ieee.org.}
\thanks{P. Bunch and S. Godsill are with the Department
of Engineering, Cambridge University, UK. email: \{pb404,sjg30\}@cam.ac.uk}% <-this % stops a space
}

@@

\begin{IEEEkeywords}
state space model, particle filter, smoothing, MCMC, Bayesian inference
\end{IEEEkeywords}

@@

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.9\columnwidth]{fig6-a.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.9\columnwidth]{fig6-b.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.9\columnwidth]{fig6-c.pdf}}
\caption{Example trajectory with observations from the two noise covariance cases. Constant likelihood contours are shown for the first and last position (dashed)}
\label{fig:example_trajectories}
\end{figure}

@@

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 1. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case1_performance}
{\scriptsize
\centering
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 0.56 & 0.96 & 0.99 & 0.00 & 2.13 \\
D-FFBS         & 0.45 & 0.76 & 0.84 & 65.88 & 20.54 \\
\hline
MH-FFBS (1)    & 0.48 & 0.81 & 0.90 & 1.80 & 13.95 \\
MH-FFBS (3)    & 0.46 & 0.78 & 0.87 & 3.89 & 17.63 \\
MH-FFBS (10)   & 0.46 & 0.77 & 0.85 & 11.20 & 19.83 \\
MH-FFBS (30)   & 0.45 & 0.76 & 0.84 & 32.05 & 20.40 \\
MH-FFBS (100)  & 0.45 & 0.76 & 0.84 & 105.12 & 20.55 \\
\hline
MH-FFBP (1)    & 0.45 & 0.75 & 0.82 & 9.20 & 44.32 \\
MH-FFBP (3)    & 0.43 & 0.73 & 0.79 & 19.23 & 70.12 \\
MH-FFBP (10)   & 0.43 & 0.72 & 0.78 & 54.33 & 90.10 \\
MH-FFBP (30)   & 0.42 & 0.71 & 0.79 & 154.47 & 96.89 \\
MH-FFBP (100)  & 0.42 & 0.70 & 0.79 & 504.58 & 98.53 \\
\hline

\end{tabular}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 2. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case2_performance}
{\scriptsize
\centering
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS             & 8.01 & 1.90 & 0.99 & 0.00 & 2.75 \\
D-FFBS         & 7.71 & 1.70 & 0.92 & 66.40 & 14.06 \\
\hline
MH-FFBS (1)    & 7.91 & 1.83 & 0.98 & 1.79 & 6.51 \\
MH-FFBS (3)    & 7.83 & 1.78 & 0.96 & 3.86 & 8.63 \\
MH-FFBS (10)   & 7.77 & 1.73 & 0.93 & 11.09 & 11.39 \\
MH-FFBS (30)   & 7.75 & 1.71 & 0.92 & 31.77 & 13.14 \\
MH-FFBS (100)  & 7.70 & 1.70 & 0.92 & 104.14 & 13.88 \\
\hline
MH-FFBP (1)    & 7.75 & 1.72 & 0.92 & 9.25 & 22.97 \\
MH-FFBP (3)    & 7.67 & 1.67 & 0.88 & 19.34 & 42.22 \\
MH-FFBP (10)   & 7.62 & 1.63 & 0.85 & 54.61 & 70.06 \\
MH-FFBP (30)   & 7.60 & 1.61 & 0.84 & 155.38 & 88.81 \\
MH-FFBP (100)  & 7.59 & 1.60 & 0.84 & 507.58 & 96.82 \\
\hline
\end{tabular}
}
\end{table}

\begin{table}[!t]%
\renewcommand{\arraystretch}{1.3}
\caption{Smoother performance measures for noise covariance case 3. All results are averaged over 100 runs, with 500 time steps in each run.}
\label{tab:case3_performance}
{\scriptsize
\centering
\begin{tabular}{|c||c|c|c|c|c|}
\hline
Algorithm & \begin{minipage}[c]{0.9cm} Position RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  Velocity RMSE \end{minipage} & \begin{minipage}[c]{0.9cm}  ENEES \end{minipage} & \begin{minipage}[c]{0.9cm}  Running Time (s) \end{minipage} & \begin{minipage}[c]{0.9cm}  Unique Particles \end{minipage} \\
\hline
FS            & 7.41 & 2.15 & 0.98 & 0.00 & 3.97 \\
D-FFBS        & 7.19 & 2.03 & 0.97 & 66.27 & 7.48 \\
\hline
MH-FFBS (1)   & 7.39 & 2.14 & 0.98 & 1.75 & 4.79 \\
MH-FFBS (3)   & 7.36 & 2.12 & 0.98 & 3.75 & 5.33 \\
MH-FFBS (10)  & 7.30 & 2.08 & 0.98 & 10.78 & 6.16 \\
MH-FFBS (30)  & 7.24 & 2.05 & 0.97 & 30.83 & 6.88 \\
MH-FFBS (100) & 7.20 & 2.04 & 0.97 & 101.02 & 7.38 \\
\hline
MH-FFBP (1)   & 7.22 & 2.05 & 0.97 & 9.12 & 12.57 \\
MH-FFBP (3)   & 7.08 & 1.98 & 0.94 & 19.01 & 22.78 \\
MH-FFBP (10)  & 6.95 & 1.92 & 0.92 & 53.64 & 44.15 \\
MH-FFBP (30)  & 6.87 & 1.88 & 0.90 & 152.42 & 70.71 \\
MH-FFBP (100) & 6.84 & 1.86 & 0.88 & 498.38 & 91.35 \\
\hline
\end{tabular}
}
\end{table}

\begin{figure}[!t]
\centering
\subfloat[Case 1]{\includegraphics[width=0.9\columnwidth]{fig7-a.pdf}}
\\
\subfloat[Case 2]{\includegraphics[width=0.9\columnwidth]{fig7-b.pdf}}
\\
\subfloat[Case 3]{\includegraphics[width=0.9\columnwidth]{fig7-c.pdf}}
\caption{Position RMSEs and running times of various smoothing algorithms with different noise covariance cases.}%
\label{fig:rmse_vs_time}%
\end{figure}

@@

\newpage
\bibliographystyle{IEEEtran}
%\bibliography{Cleanbib}
\input{MCMCsmoother.bbl}

@@

\input{IEEE-Bunch.tex}
\input{IEEE-Godsill.tex}
